---
title: "Rmarkdown"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rmarkdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)
```

To include a chart in Rmarkdown simply place the code in a code chunk/code fence.

```{r}
g2(beaver1, asp(time, temp)) %>% 
  fig_line() %>% 
  fig_point(asp(shape = "circle"))
```

## Show/Hide

One can also include "actions" in Rmarkdown documents, these are some elements of dynamism in static documents. These "actions" are tied to inputs, similar to shiny.

For instance, create an input button.

```{r}
input_button(id = "visible", label = "Toggle visibility")
```

Then tie the input button (above) to the `action_toggle_visibility` on a graph: clicking the button shows or hides the plot below.

```{r}
g2(mtcars, asp(mpg, qsec)) %>%
  fig_point() %>% 
  action_toggle_visibility("visible")
```

## Change Data

One can also create a dropdown menu with `input_select`.

```{r}
input_select(
  id = "dataset", 
  label = "Select a dataset",
  choices = c("Cars", "Flowers")
)
```

Then bind that select input with `action_select_data` to allow dynamically changing the underlying dataset used in the graph.

```{r}
generate <- function(n){
  data.frame(
    x = 1:100,
    y = runif(100, 1, n)
  )
}

g2(generate(20), asp(x, y)) %>%
  fig_point() %>% 
  action_select_data(
    "dataset", 
    datasets = list(
      Cars = generate(30),
      Flowers = generate(50)
    )
  )
```

## Filter

One can also dynamically filter the data with either `input_slider` or `input_select`.

```{r}
input_slider(
  id = "yFilter", 
  label = "Filter Y >", 
  value = 50, 
  min = 0, 
  max = 120, 
  step = 5
)
```

To filter the data, bind the `action_filter_data` to the chart.

The `operator` of the filter is combined with the value from the `input` and the `asp` to form a filter statement with the following template; `asp operator inputValue`.

For instance, below we create a filter on input `id = "yFilter"` on the column `dist` (of the `cars` dataset) with the operator `>` (greater than) will create the following filter pseudo statement: `speed > yFilterValue`.

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  fig_smooth() %>% 
  action_filter_data(
    input = "yFilter",
    asp = dist,
    operator = ">"
  )
```

The `action_filter_data` can also be bound to an `input_select`.

```{r}
input_select(
  "grp", 
  "Select a group",
  c("Group A", "Group B", "Group C")
)
```

Note the use of the `==` operator in this case.

```{r}
df <- data.frame(
  x = rep(1:100, each = 3),
  y = rnorm(300, rep(c(4,5,2), each = 100)),
  group = rep(c("Group A", "Group B", "Group C"), each = 100)
)

g2(df, asp(x, y)) %>% 
  fig_point() %>% 
  fig_smooth() %>% 
  action_filter_data(
    "grp",
    group,
    operator = "=="
  )
```

## Action

One can also use `g2Action` in a manner akin to [g2_proxy]: to dynamically add or update figures and other aspects of the chart.

```{r}
g2(mtcars, asp(mpg, qsec), elementId = "plotty") %>% 
  fig_point(config("hello"))
```

```{r}
input_button("update", "Update chart")
```

```{r}
g2_action("plotty", "update", asp(mpg), data = mtcars) %>% 
  fig_point(asp(y = drat, shape = "triangle")) %>% 
  fig_point(asp(y = wt, shape = "circle"), config("hello")) %>% 
  render()
```
