---
title: "Advanced"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(g2r)
```

## Figures

At its code G2.js comprises of just a few [primitive figures](https://g2.antv.vision/en/docs/api/advanced/register-shape).

- `fig_point`
- `fig_interval` (bar)
- `fig_line`
- `fig_polygon`
- `fig_edge`
- `fig_schema`
- `fig_area`

However, g2r provides many more. This is simply to say that all figures provided by g2r but not G2.js are actually built, under-the-hood, by the aforementioned primitive figures.

Take for instance `fig_ribbon` which G2.js does not handle out of the box. A ribbon chart is essentially an area chart that holds two `y` values for every `x`, where the first is the lower bound and the second is the higher bound.

So why add `fig_ribbon`? Well because the shape of the data that must be passed to G2.js is somewhat unwieldy.

```json
[
  [
    0,      // x
    [1, 2]  // ymin, ymax
  ],
  [
    1,      // x
    [3, 4]  // ymin, ymax
  ]
  [
    2,      // x
    [1, 5]  // ymin, ymax
  ]
]
```

Instead of using `fig_ribbon` one could simply build the a list column tibble that resembles the above and use `fig_area`.

```{r}
library(dplyr)

df <- tibble(
  x = 1:100,
  y = runif(100)
) %>% 
  mutate(
    y = lapply(y, function(x) list(x - 1, x + 1))
  )

df %>% 
  head() %>% 
  knitr::kable()
```

With the list column where the `y` column actually holds two values one can now simply use `fig_area`.

```{r}
g2(df, asp(x, y)) %>% 
  fig_area()
```

All of the custom figures provided by g2r are in the [figures.R file](https://github.com/devOpifex/g2r/blob/master/R/figures.R), feel free to take a look to learn more about how they work.

## Aspects

It may be somewhat counterintuitive at first but G2.js allows multiple "aspects" where one would often only expect one. For instance the tooltip of a visualisation can make use or present multiple variables.

```{r}
mtcars %>% 
  mutate(vs = as.factor(vs)) %>% 
  g2(asp(mpg, wt, size = qsec, tooltip = gear, tooltip = carb)) %>% 
  fig_point(asp(shape = "circle", color = vs))
```
