---
title: "Aspects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Aspects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(g2r)
```

Aspects (`asp()`) are analogous to `ggplot2::aes` but may work in somewhat different ways in places.

```{r}
library(g2r)

g2(trees, asp(Girth, Volume, size = Height)) %>% 
  fig_point(asp(shape = "circle", label = Height))
```

Aspects define the visualisation, these aspects can be further manipulated with the `gauge_*` functions.

```{r}
cb <- "(data, mappingData, index) => {
  return data.Height + 'ft'
}"

g2(trees, asp(Girth, Volume, size = Height)) %>% 
  fig_point(asp(shape = "circle", label = Height)) %>% 
  gauge_label(
    content = htmlwidgets::JS(cb), 
    style = list(fill = "darkgray")
  )
```

_Callback functions have to be wrapped with `htmlwidgets::JS`_

There are some differences with ggplot2 though, e.g.: the use of JavaScript functions as shown above. Another such difference is that one use the same aspect multiple times (not all aspects).

<details>
```{r}
df <- data.frame(
  x = c(letters, letters),
  y = runif(52),
  grp = rep(c("A", "B"), each = 2)
)
```
</details>

The `gauge` is only used when a corresponding aspect has been defined, to configure a global feature of the chart there are other functions, e.g.: `tooltip`.

<div class="panel panel-warning">
<div class="panel-heading">Warning</div>
<div class="panel-body">
The graph below is __erroneous.__
</div>
</div>

```{r}
g2(df, asp(x, y, color = grp)) %>% 
  fig_interval() %>% 
  tooltip(
    shared = TRUE,
    showMarkers = FALSE
  )
```

Some aspects (few) are defined outside of the `asp` function, e.g.: to `adjust` bars on a chart or points on a scatter plot.

```{r}
g2(df, asp(x, y, color = grp)) %>% 
  fig_interval(adjust("dodge")) %>% 
  tooltip(
    shared = TRUE,
    showMarkers = FALSE
  )
```

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point(asp(shape = "circle")) %>% 
  fig_point(adjust("jitter")) %>% 
  fig_point(adjust("jitter")) %>% 
  fig_point(adjust("jitter"))
```

Aspects also define the shape of points, lines, and areas.

```{r}
df <- data.frame(
  x = 1:100,
  y = rnorm(100, mean = rep(c(10, 14), each = 50))
)

g2(df, asp(x, y)) %>% 
  fig_smooth(asp(shape = "smooth"), method = "gaussian") %>% 
  fig_point(asp(shape = "square"))
```
