---
title: "Crosstalk"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Crosstalk}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
library(g2r)
library(plotly)
library(crosstalk)

motif_global(fontFamily = "Quicksand")
```

g2r supports [crosstalk](https://rstudio.github.io/crosstalk/) to link g2 visualisations with other [htmlwidgets](http://htmlwidgets.org/) that [supports crosstalk](https://rstudio.github.io/crosstalk/widgets.html).

<div class="panel panel-warning">
<div class="panel-heading">Warning</div>
<div class="panel-body">
Crosstalk only works with data passed to `g2`.
</div>
</div>

## Filter

For instance, one can add a g2 plot to an example from the [plotly R book](https://plotly-r.com/client-side-linking.html).

```{r, warning=FALSE, message=FALSE, error=FALSE}
library(g2r)
library(plotly)
library(crosstalk)

# plotly
tx <- highlight_key(txhousing)

# filter widgets
widgets <- bscols(
  widths = c(12, 12, 12),
  filter_select("city", "Cities", tx, ~city),
  filter_slider("sales", "Sales", tx, ~sales),
  filter_checkbox("year", "Years", tx, ~year, inline = TRUE)
)

# arrange
bscols(
  widths = c(2, 5, 5),
  widgets, 
  plot_ly(tx, x = ~date, y = ~median, showlegend = FALSE) %>% 
    add_lines(color = ~city, colors = "black"),
  g2(tx, asp(date, median, color = city)) %>% 
    fig_line() %>% 
    legend_color(FALSE)
)
```

## Select

g2r also supports the select handle so selection is communicated between widgets. Note the use of `selected`, without which selecting a point on the g2 plot (though works fine crosstalk-wise) does not highlight the stroke in black.

```{r}
shared_cars <- SharedData$new(cars)

bscols(
  plot_ly(shared_cars, x = ~speed, y = ~dist) %>% 
    add_markers(),
  g2(shared_cars, asp(speed, dist)) %>% 
    fig_point(selected(stroke = "black"))
)
```

## Customisation

The selection handle can be greatly customised to define the look of points, bars, etc when they are selected or unselected. The `crosstalk_select` function accepts the name of the attribute to change and the values this attribute should take when within selected (`on`) and outside the selection (`off`), setting `on` or `off` to `NULL` means not to change that attribute for that state.

```{r}
df <- data.frame(
  x = letters,
  y = runif(26)
)

sd <- SharedData$new(df)

bscols(
  plot_ly(sd, x = ~x, y = ~y) %>% 
    add_bars(),
  g2(sd, asp(x, y)) %>% 
    fig_interval() %>% 
    crosstalk_select("fill", on = "green", off = "grey") %>% 
    crosstalk_select("stroke", on = "black", off = "grey")
)
```

One can reproduce the effect given by plotly by playing with the opacity for instance.

```{r}
bscols(
  plot_ly(sd, x = ~x, y = ~y) %>% 
    add_bars(),
  g2(sd, asp(x, y)) %>% 
    fig_interval() %>% 
    crosstalk_select("fillOpacity", on = 1, off = .3)
)
```
