---
title: "Figures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Figures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(g2r)
```

g2r comes with a number of figures that can be used to create visualisations. However, these can be used in many different ways than what is presented here in order to produce completely different looking charts.

## Line

The line can be controlled with `shape`: `smooth`, `dot`, or `line` (default).

```{r}
df <- data.frame(
  x = 1:90,
  y = rnorm(90, mean = rep(c(65,70,75),each=30), sd = 2) 
)

g2(df, asp(x, y)) %>% 
  fig_line()
```

## Step

A step chart is a line chart with a `shape`, one of: `vh`, `hv`, `hvh`, or `vhv`.

```{r}
g2(df, asp(x, y)) %>% 
  fig_line(asp(shape = "hv"))
```

## Point

```{r}
g2(iris, asp(Sepal.Width, Sepal.Length, color = Species)) %>% 
  fig_point()
```

## Area

```{r}
blockchain <- jsonlite::fromJSON(
  "https://gw.alipayobjects.com/os/antvdemo/assets/data/blockchain.json"
)

g2(blockchain, asp(date, blockchain)) %>% 
  fig_area()
```

## Path

```{r}
df <- data.frame(
  x = runif(50),
  y = runif(50) 
)

g2(df, asp(x, y)) %>% 
  fig_path()
```

## Interval

```{r}
df <- data.frame(
  x = seq.Date(Sys.Date() - 29, Sys.Date(), by = "days"),
  y = rnorm(30, mean = rep(c(70,60),each=15), sd = 3)
)

g2(df, asp(x, y)) %>% 
  fig_interval()
```

## Polygon

```{r}
df <- expand.grid(x = letters, y = letters)
df$value <- rnorm(nrow(df))

g2(df, asp(x, y, color = value)) %>% 
  fig_polygon() %>% 
  gauge_color(c("#BAE7FF", "#1890FF", "#0050B3"))
```

## Heatmap

```{r}
g2(mtcars, asp(mpg, qsec, color = drat)) %>% 
  fig_heatmap() %>% 
  gauge_color(c("blue", "cyan", "lime", "yellow", "red"))
```

## Bin

```{r}
g2(cars, asp(speed, dist, color = count)) %>% 
  fig_bin() %>% 
  gauge_color(c("#BAE7FF", "#1890FF", "#0050B3"))
```

## Ribbon

```{r}
df <- data.frame(
 x = 1:90,
 y = rnorm(90, mean = rep(c(67,70,73),each=30), sd = 2)
)

df$ymin <- df$y - runif(90, 1, 2)
df$ymax <- df$y + runif(90, 1, 4)

g2(df, asp(x, ymin = ymin, ymax = ymax)) %>% 
  fig_line(asp(y = y)) %>% 
  fig_ribbon()
```

## Histogram

```{r}
df <- data.frame(
 grp = rep(c("A", "B"), each = 200),
   val = c(
     rnorm(200, mean = 57, sd = 5), 
     rnorm(200, mean = 53, sd = 5)
   )
)

g2(df, asp(val, color = grp)) %>% 
 fig_histogram(bin_width = 1, fillOpacity = .5)
```

## Density

```{r}
g2(iris, asp(Sepal.Length, Sepal.Width, color = Species)) %>% 
  fig_density()
```

## Boxplot

```{r}
df <- tidyr::pivot_longer(iris, -Species)

g2(df, asp(name, value, color = Species)) %>% 
 fig_boxplot(adjust("dodge"))
```

## Smooth

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  fig_smooth(asp(shape = "smooth"), method = "polynomial")
```

## Range

```{r}
df <- data.frame(
 x = 1:10,
 ymin = runif(10, 1, 5),
 ymax = runif(10, 6, 13)
)

g2(df, asp(x, ymin = ymin, ymax = ymax)) %>% 
 fig_range()
```

## Pie

```{r}
df <- data.frame(
 name = letters[1:5],
 value = runif(5)
)

g2(df, asp(y = value, color = name, label = name)) %>% 
 fig_pie()
```

## Voronoi

```{r}
df <- dplyr::tibble(
  x = runif(50, 1, 500),
  y = runif(50, 1, 500),
  value = runif(50, 1, 500)
)

g2(df, asp(x, y, color = value)) %>% 
  fig_voronoi() %>% 
  gauge_color(c("#BAE7FF", "#1890FF", "#0050B3"))
```

## Waffle

```{r}
fruits <- dplyr::tibble(
  fruit = c("Apples", "Bananas", "Pears", "Oranges"),
  value = c(.45, .15, .35, .05) * 100
)

g2(fruits, asp(value, color = fruit)) %>% 
  fig_waffle() %>% 
  motif(padding = c(10, 10, 30, 10)) %>% 
  axis_hide()
```
