---
title: "Figures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Figures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)
```

g2r comes with a number of figures that can be used to create visualisations. However, these can be used in many different ways than what is presented here in order to produce completely different looking charts; see [examples](/articles/examples.html), and [methods](/articles/methods.html).

See the [graph vignette](/articles/graph.html) for network-related figures.

## Line

The line can be controlled with `shape`: 

- `smooth`
- `dot`
- `vh`
- `hv`
- `hvh`
- `vhv`
- `dash`
- `line` (default).

```{r}
df <- data.frame(
  x = 1:99,
  y = rnorm(99, mean = rep(c(65,70,75),each=33), sd = 2) 
)

g2(df, asp(x, y)) %>% 
  fig_line()
```

## Step

A step chart is a line chart with a `shape`, one of: `vh`, `hv`, `hvh`, or `vhv`.

```{r}
g2(df, asp(x, y)) %>% 
  fig_line(asp(shape = "hv"))
```

## Point

The `shape` of the point can also be set to:

- `circle`
- `bowtie`
- `cross`
- `diamond`
- `hexagon`
- `hollow-bowtie`
- `hollow-circle` (default)
- `hollow-diamond`
- `hollow-hexagon`
- `hollow-triangle`
- `hollow-triangle-down`
- `line`
- `hyphen`
- `plus`
- `tick`
- `square`

```{r}
g2(iris, asp(Sepal.Width, Sepal.Length, color = Species)) %>% 
  fig_point()
```

## Area

The `shape` of the area can also be set to:

- `area` (default)
- `line`
- `smooth`
- `smooth-line`

```{r}
blockchain <- jsonlite::fromJSON(
  "https://gw.alipayobjects.com/os/antvdemo/assets/data/blockchain.json"
)

g2(blockchain, asp(date, blockchain)) %>% 
  fig_area()
```

## Path

```{r}
df <- data.frame(
  x = runif(50),
  y = runif(50) 
)

g2(df, asp(x, y)) %>% 
  fig_path()
```

## Interval

The `shape` of the interval can also be set to:

- `rect` (default)
- `funnel`
- `hollow-rect`
- `line`
- `pyramid`
- `tick`
- `triangle`

```{r}
df <- data.frame(
  x = seq.Date(Sys.Date() - 29, Sys.Date(), by = "days"),
  y = rnorm(30, mean = rep(c(70,60),each=15), sd = 3)
)

g2(df, asp(x, y)) %>% 
  fig_interval()
```

## Polygon

```{r}
df <- expand.grid(x = letters, y = letters)
df$value <- rnorm(nrow(df))

g2(df, asp(x, y, color = value)) %>% 
  fig_polygon() %>% 
  gauge_color_blue()
```

## Heatmap

```{r}
g2(iris, asp(Sepal.Length, Sepal.Width, color = Petal.Length)) %>% 
  fig_heatmap() %>% 
  gauge_color(c("blue", "cyan", "lime", "yellow", "red"))
```

## Bin

Use `count` (internally computed) to define the color (optional).

```{r}
g2(cars, asp(speed, dist, color = count)) %>% 
  fig_bin() %>% 
  gauge_color_blue()
```

Use `size_count` to size the bins by `count`.

```{r}
data(diamonds, package = "ggplot2")

g2(diamonds, asp(table, price, color = count)) %>% 
  fig_bin(
    type = "hex", 
    size_count = FALSE,
    stroke = "#fff"
  ) %>% 
  gauge_color_blue()
```

## Ribbon

```{r}
df <- data.frame(
 x = 1:50,
 y = rnorm(50, mean = rep(c(67,73),each=25), sd = 2)
)

df$ymin <- df$y - runif(50, 2, 3)
df$ymax <- df$y + runif(50, 2, 4)

g2(df, asp(x, ymin = ymin, ymax = ymax)) %>% 
  fig_line(asp(y = y)) %>% 
  fig_ribbon()
```

## Histogram

```{r}
df <- data.frame(
 grp = rep(c("A", "B"), each = 200),
  val = c(
    rnorm(200, mean = 57, sd = 5), 
    rnorm(200, mean = 53, sd = 5)
  )
)

g2(df, asp(val, color = grp)) %>% 
 fig_histogram(bin_width = 1, fillOpacity = .5)
```

## Density

```{r}
g2(iris, asp(Sepal.Length, Sepal.Width, color = Species)) %>% 
  fig_density()
```

## Boxplot

```{r}
df <- tidyr::pivot_longer(iris, -Species)

g2(df, asp(name, value, color = Species)) %>% 
 fig_boxplot(adjust("dodge"))
```

## Smooth

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  fig_smooth(asp(shape = "smooth"), method = "polynomial")
```

## Range

Two types: `interval` and `area`.

```{r}
df <- data.frame(
 x = 1:10,
 ymin = runif(10, 1, 5),
 ymax = runif(10, 6, 13)
)

g2(df, asp(x, ymin = ymin, ymax = ymax)) %>% 
 fig_range()
```

```{r}
g2(df, asp(x, ymin = ymin, ymax = ymax)) %>% 
 fig_range(type = "area")
```

## Pie

```{r}
df <- data.frame(
 name = letters[1:5],
 value = runif(5)
)

g2(df, asp(y = value, color = name, label = name)) %>% 
 fig_pie()
```

## Voronoi

```{r}
df <- dplyr::tibble(
  x = runif(50, 1, 500),
  y = runif(50, 1, 500),
  value = runif(50, 1, 500)
)

g2(df, asp(x, y, color = value)) %>% 
  fig_voronoi() %>% 
  gauge_x_linear(nice = FALSE) %>% 
  gauge_y_linear(nice = FALSE) %>% 
  gauge_color_blue()
```

## Waffle

```{r}
fruits <- dplyr::tibble(
  fruit = c("Apples", "Bananas", "Pears", "Oranges"),
  value = c(.45, .15, .35, .05) * 100
)

g2(fruits, asp(value, color = fruit)) %>% 
  fig_waffle() %>% 
  motif(padding = c(10, 10, 30, 10)) %>% 
  axis_hide()
```

## Rug

```{r}
g2(mtcars, asp(wt, mpg)) %>% 
  fig_point() %>% 
  fig_smooth(asp(shape = "smooth"), method = "polynomial") %>% 
  fig_rug(asp(size = 10)) %>% 
  fig_rug(asp(size = 10), axis = "y")
```

## Candle

```{r}
wallgreens  <- tidyquant::tq_get("WBA", from = Sys.Date() - 90)

cb <- htmlwidgets::JS(
  "(trend) => {
    if(trend == 'Up')
      return 'green';
    
    return 'red';
  }"
)

g2(wallgreens, asp(date, open = open, close = close, high = high, low = low)) %>% 
  fig_candle() %>% 
  gauge_x_time_cat() %>% 
  gauge_color(cb)
```

## Error bars

```{r}
df <- data.frame(
  x = as.factor(c(1:10, 1:10)),
  y = runif(20, 15, 25),
  grp = rep(c("A", "B"), each = 2)
)

df$ymin <- df$y - runif(20, 1, 3)
df$ymax <- df$y + runif(20, 1, 3)

g2(df, asp(x = x, color = grp)) %>% 
  fig_error(
    asp(ymin = ymin, ymax = ymax, size = 10), 
    adjust("dodge")
  ) %>% 
  fig_interval(
    asp(y = y), 
    adjust("dodge"),
    fillOpacity = .4
  ) 
```

## Contour

```{r}
data(faithfuld, package = "ggplot2")

g2(faithfuld, asp(waiting, eruptions, z = density)) %>% 
  fig_contour(
    binwidth = 0.001,
    colors = c("#440154FF", "#21908CFF", "#FDE725FF")
  )
```

```{r}
g2(faithfuld, asp(eruptions, waiting, z = density)) %>% 
  fig_contour(
    type = "filled", 
    colors = c("#000004FF", "#B63679FF", "#FCFDBFFF")
  ) %>% 
  gauge_x_linear(nice = FALSE) %>% 
  gauge_y_linear(nice = FALSE)
```

## Segments

```{r}
seg <- df <- data.frame(
  x = c(24, 23),
  y = c(70, 54),
  xend = c(17, 24),
  yend = c(50, 93)
)

g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  fig_segment(
    asp(x = x, y = y, xend = xend, yend = yend),
    data = seg
  )
```

<a class="btn btn-default" href="quick.html">Explore quick plots</a>
