---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)
library(ggplot2)
```

g2r is an interface to the [G2.js](https://g2.antv.vision/en) JavaScript visualisation library. G2.js is itself a Grammar of Graphics (GG ~= 2G) though some things differ from R's common understanding of such grammar as implemented in [ggplot2](https://ggplot2.tidyverse.org/), some things will be similar to ggplot2 in places.

- `ggplot2::ggplot` -> `g2`
- `ggplot2::aes` -> `asp`
- `ggplot2::scale_*` -> `gauge_*`
- `ggplot2::geom_*` -> `fig_*`
- `ggplot2::facet_*` -> `planes_*`
- `ggplot2::theme_*` -> `motif_*`

The "localisation" or "translation" of the ggplot2 grammar is not just a gimmick it also allows avoiding having one package clash with the other.

## Initialise

Like with ggplot2, one creates visualisations by layering figures (geometries) defined by aspects (aesthetics).

<div class="row">
<div class="col-sm-6">
<strong>ggplot2</strong>
```{r, fig.height=9, message=FALSE, error=FALSE, warning=FALSE}
ggplot(cars, aes(speed, dist)) + 
  geom_point() +
  geom_smooth(method = "lm")
```
</div>
<div class="col-sm-6">
<strong>g2r</strong>
```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  fig_smooth()
```
</div>
</div>

## Gauge

Similarly to ggplot2, axis of the visualisation can be modified with `gauge_*` (scales in ggplot2).

<div class="row">
<div class="col-sm-6">
<strong>ggplot2</strong>
```{r, fig.height=9, message=FALSE, error=FALSE, warning=FALSE}
ggplot(iris, 
    aes(Sepal.Length, Sepal.Width, color = Petal.Width)
  ) + 
  geom_point(aes(size = Sepal.Width)) +
  scale_color_viridis_c()
```
</div>
<div class="col-sm-6">
<strong>g2r</strong>
```{r}
g2(iris, 
    asp(Sepal.Length, Sepal.Width, color = Petal.Width)
  ) %>% 
  fig_point(asp(size = Sepal.Width)) %>% 
  gauge_color_viridis()
```
</div>
</div>

<a class="btn btn-default" href="gauges.html">Gauges vignette</a>

## Aspects

As in ggplot2, other aspects of the visualisation can be defined. Unlike ggplot2 though, whether these aspects are columns from the data or constants they can only be specified within `asp`.

```{r}
data(penguins, package = "palmerpenguins")
```

<div class="row">
<div class="col-sm-6">
<strong>ggplot2</strong>
```{r, fig.height=9, message=FALSE, error=FALSE, warning=FALSE}
ggplot(penguins, 
    aes(bill_length_mm, bill_depth_mm, color = island)
  ) + 
  geom_point(aes(shape = island)) 
```
</div>
<div class="col-sm-6">
<strong>g2r</strong>
```{r}
g2(penguins, 
    asp(bill_length_mm, bill_depth_mm, color = island)
  ) %>% 
  fig_point(asp(shape = island)) 
```
</div>
</div>

<a class="btn btn-default" href="aspects.html">Aspects vignette</a>

## Color = Group

Where one might use the `group` aesthetic in ggplot2 one will want to use `color` in g2r; it'll define both the colour and the group.

```{r}
g2(iris, asp(Sepal.Length, Sepal.Width, color = Species)) %>% 
  fig_density()
```

## Adjust

In order to stack bars, or place bars side-by-side, or jitter points one must use the `adjust` function.

```{r}
g2(mtcars, asp(mpg, qsec)) %>% 
  fig_point(asp(shape = "circle")) %>% 
  fig_point(adjust("jitter"))
```

<a class="btn btn-default" href="adjust.html">Adjust vignette</a>

## Planes

G2r also comes with the equivalent of ggplot2's facets, here they are named `planes`.

```{r}
g2(iris, asp(Sepal.Length, Sepal.Width, color = Species)) %>% 
  fig_point(asp(shape = "circle")) %>% 
  planes(~Species, type = "tree")
```

<a class="btn btn-default" href="planes.html">Planes vignette</a>

## Quick plots

There is also a function to quickly draw plots based on the class of the object it receives: `qg2`.

```{r}
model <- lm(mpg ~ wt + cyl + disp + gear + hp + am, data = mtcars)

qg2(model)
```

<a class="btn btn-default" href="quick.html">Quick plots vignette</a>

## Recipes

Generally g2r functions accept data in the form of data.frames or tibbles but it will attempt to transform other objects to (generally) data.frames. 

```{r, error=FALSE, message=FALSE, warning=FALSE}
library(forecast)

ts <- AirPassengers %>%
  stlf(lambda=0)
 
g2(ts, asp(x)) %>% 
  fig_line(asp(y = y)) %>% 
  fig_line(asp(y = mean)) %>% 
  fig_ribbon(asp(ymin = lower_80, ymax = upper_80)) %>% 
  fig_ribbon(asp(ymin = lower_95, ymax = upper_95)) %>% 
  tooltip(shared = TRUE)
```

<a class="btn btn-default" href="recipes.html">Recipes vignette</a>
