---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(g2r)
```

g2r is an interface to the [G2.js](https://g2.antv.vision/en) JavaScript visualisation library. G2.js is itself a Grammar of Graphics (GG ~= 2G) though rather different from R's common understanding of such grammar from [ggplot2](https://ggplot2.tidyverse.org/).

g2r's API is halfway between G2.js and ggplot2; some things will be similar to ggplot2 in places.

- `ggplot2::ggplot` -> `g2`
- `ggplot2::aes` -> `asp`
- `ggplot2::scale_*` -> `gauge_*`
- `ggplot2::geom_*` -> `fig_*`
- `ggplot2::facet_*` -> `planes_*`
- `ggplot2::theme_*` -> `motif_*`

Like with ggplot2, one creates visualisations by layering figures (geometries) defines by aspects (aesthetics).

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  fig_smooth() 
```

Similarly to ggplot2, axis of the visualisation can be modified with `gauge_*` (scales in ggplot2).

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  fig_smooth(method = "polynomial") %>% 
  gauge_y_log()
```

As in ggplot2, other aspects of the visualisation can be defined. Unlike ggplot2 though, whether these aspects are columns from the data or constants they can only be specified within `asp`.

```{r}
g2(cars, asp(speed, dist, shape = "circle")) %>% 
  fig_point(asp(color = dist, size = dist)) %>% 
  gauge_color(c("#BAE7FF", "#1890FF", "#0050B3"))
```
