---
title: "Graph"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Graph}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(g2r)

motif_global(fontFamily = "Quicksand")
```

One can plot networks by either constructing the `data.frame`s of nodes and edges (with `x` and `y` coordinates) or use [igraph](https://igraph.org/r/) objects.

## igraph

If the visualisation was initialised with an object of class `igraph` then the `layout_igraph` function can be used to compute the coordinates of nodes and edges.

The `layout_igraph` function accepts a `method` which accepts an igraph layout function.

```{r}
library(g2r)

ig <- igraph::make_full_graph(20)

g2(ig, asp(x, y)) %>%
  layout_igraph(method = igraph::layout_in_circle) %>% 
  fig_edge() %>% 
  fig_point(asp(shape = "circle")) %>% 
  axis_hide()
```

## Layout

You can also use the `layout_arc` function to layout the node in an arc.

```{r}
ig <- igraph::erdos.renyi.game(100, 1/100)

g2(ig, asp(x, y)) %>% 
  layout_arc() %>% 
  fig_edge(
    asp(
      color = source, 
      shape = "arc"
    ), 
    opacity = .3
  ) %>% 
  fig_point(
    asp(
      color = id, 
      shape = "circle", 
      size = value,
      label = id
    )
  ) %>% 
  coord_type("polar") %>% 
  coord_reflect("y") %>% 
  axis_hide() %>% 
  gauge_label(labelEmit = TRUE) %>% 
  motif(padding = c(30, 5, 75, 5))
```

Similar as above but without the polar coordinates.

```{r}
ig <- igraph::erdos.renyi.game(100, 1/100)

g2(ig, asp(x, y)) %>% 
  layout_arc(marginRatio = .5) %>% 
  fig_edge(
    asp(
      color = source, 
      shape = "arc",
      tooltip = source,
      tooltip = target
    ), 
    opacity = .3
  ) %>% 
  fig_point(
    asp(
      color = id, 
      shape = "circle", 
      size = value,
      label = id
    )
  ) %>% 
  axis_hide() %>% 
  gauge_label(
    offset = -10, 
    rotate = pi / 2,
    style = list(
      textAlign = "left",
      fontSize = 8
    )
  ) %>% 
  motif(padding = c(20, 20, 30)) %>% 
  legend_size(FALSE) %>% 
  legend_color(FALSE)
```

## Data.frames

You can also use data.frames but then will have to compute the coordinates for the layout manually. For the edges these coordinates, for the edges, must be list columns.

- `x`: source, target x position
- `y`: source, target y position

```{r}
# edges
edges <- data.frame(
  source = sample(letters, 26),
  target = sample(letters, 26)
)

edges$x <- lapply(1:26, function(i){
  c(runif(1, 1, 10), runif(1, 1, 10))
})

edges$y <- lapply(1:26, function(i){
  c(runif(1, 1, 10), runif(1, 1, 10))
})

edges %>% 
  head() %>% 
  knitr::kable()
```

These can then be used as `x` and `y` aspects.

```{r}
g2(asp(x, y)) %>% 
  fig_edge(data = edges) %>% 
  axis_hide()
```
