---
title: "Info"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Info}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(g2r)
```

The `info_*` family of functions allows annotating visualisations.

## Marker

One can use data to place informational annotations.

```{r}
library(g2r)

data(penguins, package = 'palmerpenguins')

samp <- penguins[sample(nrow(penguins), 10), ]
samp$cnt <- letters[1:10]

g2(penguins, asp(body_mass_g, flipper_length_mm)) %>% 
  fig_point(asp(color = sex)) %>% 
  info_marker(
    asp(body_mass_g, flipper_length_mm, content = cnt), 
    top = TRUE,
    data = samp
  )
```

## Horizontal & Vertical Lines

There are convenience functions to draw vertical and horizontal lines.

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  info_hline(asp(y = 43, content = "Mean Distance")) %>% 
  info_vline(asp(x = 15, content = "Mean Speed"))
```

Otherwise lines can be specified by defining the start (`x`, `y`) and end (`xend`, `yend`) of the line.

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  info_line(
    asp(
      x = 0, y = 0, 
      xend = "max", yend = "max",
      content = "A diagonal line"
    )
  )
```

## Types

There are a number of informational annotations:

- `text`
- `image`
- `arc`
- `line`
- `region`
- `region_filter`
- `data_marker`
- `data_region`
- `shape`
- `html`

## Region filter

The area and line charts are actually white (`asp(color = "white")`), the color is actually applied with the "region filter."

```{r}
df <- data.frame(
  x = 1:100,
  y = runif(100, -5, 5)
)

g2(df, asp(x, y, color = "white", shape = "smooth")) %>% 
  fig_area() %>% 
  fig_line() %>% 
  info_region_filter(
    asp(
      x = "min", y = 0, 
      xend = "max", yend = "min"
    ), 
    top = TRUE,
    color = "red"
  ) %>% 
  info_region_filter(
    asp(
      x = "min", y = "max", 
      xend = "max", yend = 0
    ), 
    top = TRUE,
    color = "green"
  ) %>% 
  gauge_y_linear(min = -7, max = 7)
```

## Text

Positional aspects (`x`, `y`, `xend`, `yend`) accept column names, string, integers and the following key terms: `min`, `max`, `median`, `start`, `end`.

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  info_text(
    asp(x = "median", y = "median"),
    content = "Median"
  )
```

## Region

Highlight a region.

```{r}
g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  info_region(
    asp(
      x = 10, y = "max",
      xend = 20, yend = "min"
    )
  )
```
