---
title: "Interplay & State"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interplay & State}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(g2r)

motif_global(fontFamily = "Quicksand")
```

One can control the state of the chart depending on the interactions (referred to as interplay in g2r).

## State

Use the functions `selected` and `active` on a figure to customise aesthetics based on the state of the visualisation or elements it comprises.

```{r}
df <- data.frame(
 x = letters,
 y = runif(26)
)
```

For instance, on the graph below the bars are highlighted orange on click.

```{r}
library(g2r)

g2(df, asp(x, y)) %>%
 fig_interval(
   selected(fill = "orange")
 ) %>% 
 interplay("element", "selected")
```

## Interplay

Some interactions work at the level of the chart while others will work at the level of the figure, e.g.: `brush` (click and drag to select an area and filter the data points).

```{r}
g2(cars, asp(speed, dist)) %>% 
 fig_point(asp(interplay = "brush"))
```

Alternatively one can use `brush-visible` to, instead of filtering the data points, on show the selected points, hiding others.

```{r}
g2(cars, asp(speed, dist)) %>% 
 fig_point(asp(interplay = "brush-visible"))
```

## Register

G2.js comes with basic interplays out-of-the-box most of the time one will want to register an interplay and bind it to a figure.

```{r}
df <- data.frame(
 x = c(letters, letters),
 y = runif(52),
 grp = c(rep("a", 26), rep("b", 26))
)

g2(df, asp(x, y, color = grp), elementId = "x") %>% 
 fig_interval(
   asp(interplay = "element-highlight-by-color"),
   adjust("dodge")
 ) %>%  
 register_interplay(
   "element-highlight-by-color",
     start = list(
       list(
         trigger = 'element:mouseenter', 
         action = 'element-highlight-by-color:highlight'
       )
     ),
     end = list(
       list(
         trigger = 'element:mouseleave', 
         action = 'element-highlight-by-color:reset'
       )
     )
   )
```

<div class="panel panel-warning">
<div class="panel-heading">Warning</div>
<div class="panel-body">
Make sure that registered interplay have a `start`, and an `end`, omitting these often causes odd behaviour or bugs.
</div>
</div>
