---
title: "Maps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)
```

<div class="panel panel-warning">
<div class="panel-heading">Warning</div>
<div class="panel-body">
Maps are still experimental dot not perform very well.
</div>
</div>

The function `fig_map` accepts multiple dat formats. Beware of the size and level of details of these maps as they can seriously impact performances.

## sf

The function accepts `sf` objects.

```{r}
nc <- sf::st_read(system.file("shape/nc.shp", package="sf"))

g2() %>% 
  fig_map(asp(color = AREA, tooltip = NAME), map = nc) %>% 
  axis_hide() %>% 
  gauge_color(c("#0D0887FF", "#CC4678FF", "#F0F921FF")) %>% 
  tooltip(
    marker = FALSE,
    showTitle = FALSE
  ) %>% 
  aka(NAME_3, "Province")
```

```{r}
# remotes::install_github("JohnCoene/globe4r")
data(cables, package = "globe4r")

g2() %>%
  fig_map(fill = "grey", asp(tooltip = name)) %>% 
  fig_path(data = cables, asp(X, Y, color = L1, shape = "smooth")) %>% 
  legend_color(FALSE) %>% 
  axis_hide() %>% 
  tooltip(
    showTitle = FALSE,
    marker = FALSE
  )
```

## GADM

There is a convenience function to retrieve [GADM](https://gadm.org/) data but will work with the `raster::getData` function as well.

```{r}
belgium <- get_gadm_data("BEL", level = 3)

g2() %>% 
  fig_map(
    asp(tooltip = NAME_3),
    stroke = "#fff", fill = "gray", map = belgium
  ) %>% 
  axis_hide() %>% 
  tooltip(
    marker = FALSE,
    showTitle = FALSE
  ) %>% 
  aka(NAME_3, "Province")
```

## Map data

There is also a `get_map_data` which resembles `ggplot2::map_data`.

```{r}
china <- get_map_data("China")

g2() %>% 
  fig_map(map = china, asp(tooltip = level)) %>% 
  axis_hide() %>% 
  tooltip(
    marker = FALSE,
    showTitle = FALSE
  ) 
```
