---
title: "Maps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)
```

<div class="panel panel-warning">
<div class="panel-heading">Warning</div>
<div class="panel-body">
Maps are still experimental dot not perform very well.
</div>
</div>

The function `fig_map` accepts multiple dat formats. Beware of the size and level of details of these maps as they can seriously impact performances.

## sf

The function accepts `sf` objects.

```{r}
nc <- sf::st_read(system.file("shape/nc.shp", package="sf"))

g2() %>% 
  fig_map(asp(color = AREA), map = nc) %>% 
  axis_hide() %>% 
  gauge_color(c("#0D0887FF", "#CC4678FF", "#F0F921FF"))
```

## GADM

There is a convenience function to retrieve [GADM](https://gadm.org/) data but will work with the `raster::getData` function as well.

```{r}
belgium <- get_gadm_data("BEL", level = 3)

g2() %>% 
  fig_map(stroke = "#fff", fill = "gray", map = belgium) %>% 
  axis_hide()
```

## Map data

There is also a `get_map_data` which resembles `ggplot2::map_data`.

```{r}
china <- get_map_data("China")

g2() %>% 
  fig_map(map = china) %>% 
  axis_hide()
```
