---
title: "Methods"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)
```

The `g2` function generally accepts a `data.frame` or `tibble` but can also accept other types of objects, as shown in the [graph](/articles/graph.html) vignettes where it works on objects of class `igraph`.

These functions use the `to_g2r` method internally to obtain an object that the package can process and serialise to JSON, this is generally a `tibble` at the exception of the edge case. This function is exported so one can observe which variables will be made available to use in `asp()` for the various figures.

For instance, running `to_g2r` on an object of class `loess` returns the following `tibble`.

```{r}
data(mpg, package = "ggplot2")

smooth <- loess(hwy ~ displ, data = mpg, span = .3)

to_g2r(smooth) %>% 
  head() %>% 
  knitr::kable()
```

## Loess

```{r}
g2(smooth, asp(displ)) %>% 
  fig_point(asp(y = hwy, shape = "circle")) %>% 
  fig_line(asp(y = .fitted)) %>% 
  fig_ribbon(asp(ymin = .lower, ymax = .upper, shape = "smooth"))
```

## Linear model

```{r}
fit <- lm(dist ~ speed, data = cars)

g2(fit, asp(speed)) %>% 
  fig_point(asp(y = dist, shape = "circle")) %>% 
  fig_line(asp(y = .fitted)) %>% 
  fig_ribbon(asp(ymin = .lower, ymax = .upper, shape = "smooth"))
```

## Ts

```{r}
g2(AirPassengers, asp(x, y)) %>% 
  fig_line() %>% 
  fig_area()
```

## Forecast

```{r}
library(forecast)

ts <- USAccDeaths %>%
  stl(s.window='periodic') %>%
  forecast()
 
g2(ts, asp(x)) %>% 
  fig_line(asp(y = y)) %>% 
  fig_line(asp(y = mean)) %>% 
  fig_ribbon(asp(ymin = lower_80, ymax = upper_80)) %>% 
  fig_ribbon(asp(ymin = lower_95, ymax = upper_95))
```

## Survival

```{r}
library(survival)

data(veteran)

km_fit <- survfit(Surv(time, status) ~ trt, data = veteran)

g2(km_fit, asp(time, color = "strata", shape = "vh")) %>% 
  fig_line(asp(y = estimate)) %>% 
  fig_ribbon(asp(ymin = conf.low, ymax = conf.high)) %>% 
  fig_point(asp(y = n.censor.y, shape = "circle"), stroke = "black")
```
