---
title: "Methods"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)
```

The `g2` function generally accepts a `data.frame` or `tibble` but can also accept other types of objects, as shown in the [graph](/articles/graph.html) vignettes where it works on objects of class `igraph`.

These functions use the `to_g2r` method internally to obtain an object that the package can process and serialise to JSON, this is generally a `tibble` at the exception of the edge case. This function is exported so one can observe which variables will be made available to use in `asp()` for the various figures.

For instance, running `to_g2r` on an object of class `loess` returns the following `tibble`.

```{r}
data(mpg, package = "ggplot2")

smooth <- loess(hwy ~ displ, data = mpg, span = .3)

to_g2r(smooth) %>% 
  head() %>% 
  knitr::kable()
```

## Loess

```{r}
g2(smooth, asp(displ)) %>% 
  fig_point(asp(y = hwy, shape = "circle")) %>% 
  fig_line(asp(y = .fitted)) %>% 
  fig_ribbon(asp(ymin = .lower, ymax = .upper, shape = "smooth"))
```

## Linear model

```{r}
fit <- lm(dist ~ speed, data = cars)

g2(fit, asp(speed)) %>% 
  fig_point(asp(y = dist, shape = "circle")) %>% 
  fig_line(asp(y = .fitted)) %>% 
  fig_ribbon(asp(ymin = .lower, ymax = .upper, shape = "smooth"))
```

## Ts

```{r}
g2(AirPassengers, asp(x, y)) %>% 
  fig_line() %>% 
  fig_area()
```

# Mts

```{r}
deaths <- cbind(ldeaths, fdeaths, mdeaths)

g2(deaths, asp(x)) %>% 
  fig_line(asp(y = ldeaths, color = "#e63946")) %>% 
  fig_line(asp(y = fdeaths, color = "#a8dadc")) %>%
  fig_line(asp(y = mdeaths, color = "#1d3557"))
```

# Xts

```{r, warning=FALSE, message=FALSE, error=FALSE}
library(quantmod)

aapl <- getSymbols("AAPL", env=NULL)

g2(aapl, asp(x, open = AAPL.Open, close = AAPL.Close)) %>% 
  fig_candle(asp(high = AAPL.High, low = AAPL.Low))
```

```{r}
library(quantmod)

rate <- getFX("EUR/CHF", auto.assign = FALSE)

g2(rate, asp(x, EUR.CHF)) %>% 
  fig_line()
```

## Forecast

```{r}
library(forecast)

ts <- USAccDeaths %>%
  stl(s.window='periodic') %>%
  forecast()
 
g2(ts, asp(x)) %>% 
  fig_line(asp(y = y)) %>% 
  fig_line(asp(y = mean)) %>% 
  fig_ribbon(asp(ymin = lower_80, ymax = upper_80)) %>% 
  fig_ribbon(asp(ymin = lower_95, ymax = upper_95))
```

## Survival

```{r}
library(survival)

data(veteran)

km_fit <- survfit(Surv(time, status) ~ trt, data = veteran)

g2(km_fit, asp(time, color = "strata", shape = "vh")) %>% 
  fig_line(asp(y = estimate)) %>% 
  fig_ribbon(asp(ymin = conf.low, ymax = conf.high)) %>% 
  fig_point(asp(y = n.censor.y, shape = "circle"), stroke = "black")
```

## Acf

```{r}
cc <- acf(lh, plot = FALSE)

g2(cc) %>% 
  fig_interval(asp(lag, acf, size = 2))
```

## Matrices

```{r}
correl_mat <- cor(mtcars)

g2(correl_mat) %>% 
  fig_polygon(asp(Var1, Var2, color = Freq)) %>% 
  gauge_color(c("#fae0e4", "#ff85a1", "#ff0a54"))
```

```{r}
g2(volcano) %>% 
  fig_polygon(asp(Var1, Var2, color = Freq)) %>% 
  gauge_color(c("#ffba08", "#dc2f02", "#03071e"))
```
