---
title: "Recipes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Recipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)
```

The `g2` function generally accepts a `data.frame` or `tibble` but can also accept other types of objects, as shown in the [graph](/articles/graph.html) vignettes where it works on objects of class `igraph`.

Note that some of the charts produced can also be made using `qg2`, see the [quick plots](/articles/quick.html) vignette.

These functions use the `to_g2r` method internally to obtain an object that the package can process and serialise to JSON, this is generally a `tibble` at the exception of the edge case. This function is exported so one can observe which variables will be made available to use in `asp()` for the various figures.

For instance, running `to_g2r` on an object of class `loess` returns the following `tibble`.

```{r}
data(mpg, package = "ggplot2")

smooth <- loess(hwy ~ displ, data = mpg, span = .3)

to_g2r(smooth) %>% 
  head() %>% 
  knitr::kable()
```

Variables in the table able above are therefore available as `asp()`; see chart below.

## Loess

```{r}
g2(smooth, asp(displ)) %>% 
  fig_point(asp(y = hwy, shape = "circle")) %>% 
  fig_line(asp(y = .fitted, shape = "smooth")) %>% 
  fig_ribbon(asp(ymin = .lower, ymax = .upper, shape = "smooth"))
```

## Linear model

```{r}
fit <- lm(dist ~ speed, data = cars)

g2(fit, asp(speed)) %>% 
  fig_point(asp(y = dist, shape = "circle")) %>% 
  fig_line(asp(y = .fitted)) %>% 
  fig_ribbon(asp(ymin = .lower, ymax = .upper, shape = "smooth"))
```

## Ts

```{r}
g2(AirPassengers, asp(x, y)) %>% 
  fig_line() %>% 
  fig_area()
```

# Mts

```{r}
deaths <- cbind(ldeaths, fdeaths, mdeaths)

g2(deaths, asp(x)) %>% 
  fig_line(asp(y = ldeaths, color = "#e63946")) %>% 
  fig_line(asp(y = fdeaths, color = "#a8dadc")) %>%
  fig_line(asp(y = mdeaths, color = "#1d3557")) %>% 
  tooltip(shared = TRUE)
```

```{r}
deaths <- rbind(ldeaths, fdeaths, mdeaths)

g2(deaths, asp(Var2, Freq, color = Var1)) %>% 
  fig_area() %>% 
  planes(~Var1, rows = 3, cols = 1, type = "list", padding = 20) %>% 
  motif(padding = 30) %>% 
  tooltip(shared = TRUE)
```

# Xts

```{r, warning=FALSE, message=FALSE, error=FALSE}
library(quantmod)

aapl <- getSymbols("AAPL", env=NULL)

aapl %>%
  head(50) %>% 
  g2(asp(x, open = AAPL.Open, close = AAPL.Close)) %>% 
  fig_candle(asp(high = AAPL.High, low = AAPL.Low))
```

```{r}
library(quantmod)

rate <- getFX("EUR/CHF", auto.assign = FALSE)

g2(rate, asp(x, EUR.CHF)) %>% 
  fig_line()
```

## Forecast

```{r, error=FALSE, message=FALSE, warning=FALSE}
library(forecast)

ts <- USAccDeaths %>%
  stl(s.window='periodic') %>%
  forecast()
 
g2(ts, asp(x)) %>% 
  fig_line(asp(y = y)) %>% 
  fig_line(asp(y = mean)) %>% 
  fig_ribbon(
    asp(ymin = lower_80, ymax = upper_80),
    alias = "80"
  ) %>% 
  fig_ribbon(
    asp(ymin = lower_95, ymax = upper_95),
    alias = "90"
  )
```

## Survival

```{r}
library(survival)

data(veteran)

km_fit <- survfit(Surv(time, status) ~ trt, data = veteran)

g2(km_fit, asp(time, color = strata, shape = "vh")) %>% 
  fig_line(asp(y = estimate)) %>% 
  fig_ribbon(asp(ymin = conf.low, ymax = conf.high)) %>% 
  fig_point(asp(y = n.censor.y, shape = "circle"), stroke = "black")
```

## Acf

```{r}
cc <- acf(lh, plot = FALSE)

g2(cc) %>% 
  fig_interval(asp(lag, acf, shape = "line"))
```

## Matrices

```{r}
correl_mat <- cor(mtcars)

g2(correl_mat) %>% 
  fig_polygon(asp(Var1, Var2, color = Freq)) %>% 
  gauge_color(c("#fae0e4", "#ff85a1", "#ff0a54"))
```

```{r}
g2(volcano) %>% 
  fig_polygon(asp(Var1, Var2, color = Freq)) %>% 
  gauge_color(c("#ffba08", "#dc2f02", "#03071e"))
```

## Roc Curve

```{r}
library(yardstick)

data(hpc_cv)

hpc_cv %>%
  dplyr::group_by(Resample) %>%
  roc_curve(obs, VF:L) %>% 
  g2(asp(specificity, sensitivity, color = Resample)) %>% 
  fig_path() %>% 
  gauge_y_linear(min = 0, max = 1) %>% 
  planes(
    ~.level, 
    type = "list", 
    cols = 2, 
    rows = 2,
    padding = 25
  )
```

## Boxplot + Jitter

```{r}
df <- tidyr::pivot_longer(iris, -Species) 

g2(df, asp(name, value, color = Species)) %>%  
  fig_boxplot(adjust("dodge")) %>% 
  fig_point(
    asp(shape = "circle"),
    fillOpacity = .5,
    stroke = 0,
    adjust("dodge"), adjust("jitter")
  )
```

## Stl

```{r}
decomposed <- stl(mdeaths, "per")

g2(decomposed, asp(x, value, color = variable)) %>% 
  fig_line() %>% 
  planes(~variable, cols = 1, rows = 4, type = "list", padding = 20) %>% 
  motif(padding = c(10, 10, 30, 30))
```

## T SNE

```{r}
library(Rtsne)

# remove uniques
iris_unique <- unique(iris)

set.seed(42L)
tsne <- Rtsne(as.matrix(iris_unique[,1:4]))

df <- as.data.frame(tsne$Y)
df$specie <- iris_unique$Species

g2(df, asp(V1, V2, color = specie)) %>% 
  fig_point(asp(shape = "circle"))
```

## Missing data

Similar to [naniar](https://naniar.njtierney.com/) `geom_miss_point`.

```{r}
miss <- to_g2r(airquality) %>% 
  dplyr::filter(is.na(Ozone) | is.na(Solar.R))

g2(airquality, asp(Ozone, Solar.R)) %>% 
  fig_point() %>% 
  fig_rug(
    asp(shape = "circle"), 
    fill = "#ff7d7d", 
    fillOpacity = .5,
    stroke = 0,
    data = miss
  ) %>% 
  fig_rug(
    asp(shape = "circle"), 
    fill = "#ff7d7d",
    fillOpacity = .5, 
    stroke = 0,
    data = miss, 
    axis  = "y"
  )
```
