---
title: "Shiny"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Shiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)
```


g2r is well integrated with shiny, nearly every function of the package can be used on a `g2_proxy` for smooth shiny transitions.

## Proxy

A quick word on the aforementioned "proxy." A proxy is a representation of _an already drawn_ plot and allows dynamically interacting with the plot. This only works in shiny.

Proxies enable changing aspects of the charts on the fly to add a figure, or remove one for instance. This can of course be done without the use of proxy but then one is likely redrawing the entire chart instead of just adding a single figure, this is less performant and visually less pleasing (animations, etc.).

## Add Figures

To dynamically add one or more figures by creating a proxy with `g2_proxy`: the function is identical to `g2` except it takes the id of the plot it must proxy as first argument.

Finally, use the `render` function on the proxy to render the changes, additions, deletions, etc. This allows executing multiple actions at one.

```r
library(g2r)
library(shiny)

df <- data.frame(
  x = 1:100,
  y = runif(100)
)

ui <- fluidPage(
  actionButton("add", "add figure"),
  g2Output("plot")
)

server <- function(input, output){

  output$plot <- renderG2({
    g2(df, asp(x, y)) %>% 
      fig_point()
  })

  observeEvent(input$add, {
    dat <- data.frame(
      x = 1:100,
      y = runif(100)
    )

    g2_proxy("plot", data = dat) %>% 
      fig_point(asp(x, y, shape = "circle")) %>% 
      render()
  })

}

shinyApp(ui, server)
```

## Update Figures

To update figures one must make use of the `config` function to assign a unique identifier to a figure, then refer the same id in the proxy.

```r
library(g2r)
library(shiny)

df <- data.frame(
  x = 1:100,
  y = runif(100, 10, 20),
  z = runif(100, 15, 22)
)

ui <- fluidPage(
  actionButton("update", "Update"),
  g2Output("plot")
)

server <- function(input, output){

  output$plot <- renderG2({
    g2(df, asp(x, y)) %>% 
      fig_point(config("hello")) %>% 
      fig_point(
        asp(y = z, shape = "circle"), 
        config("world")
      )
  })

  observeEvent(input$update, {
    dat <- data.frame(
      x = 1:100,
      y = runif(100, 10, 20),
      z = runif(100, 15, 22)
    )

    g2_proxy("plot", asp(x, y), data = dat) %>% 
      fig_point(config("hello")) %>% 
      fig_point(
        asp(y = z, shape = "circle"), 
        config("world")
      ) %>% 
      render()
  })

}

shinyApp(ui, server)
```

## Remove Figure

Figures can be removed from the visualisation with `remove_figure`; it takes either the numeric index of the figure (layer number) or the name/id of the figure (as set by `config`).

```r
library(shiny)

df <- data.frame(
  x = 1:100,
  a = runif(100),
  b = runif(100),
  c = runif(100)
)

ui <- fluidPage(
  actionButton("rm", "remove a figure"),
  g2Output("plot")
)

server <- function(input, output){

  output$plot <- renderG2({
    g2(df, asp(x, shape = "circle")) %>% 
      fig_point(asp(y = a, color = "#ffadad")) %>% 
      fig_point(asp(y = b, color = "#a0c4ff")) %>% 
      fig_point(asp(y = c, color = "#ffc6ff"))
  })

  observeEvent(input$rm, {
    i <- sample(1:3, 1)

    g2_proxy("plot") %>% 
      remove_figure(i)
  })

}

shinyApp(ui, server)
```

## Events

The improve performances, events are not captured by default. These can be handled with the `capture_event` function. There are a large number of events that can be observed, they are listed in the [official documentation](https://g2.antv.vision/en/docs/api/general/event).

The `capture_event` function accepts three arguments, the plot objects, the event to observe, and the callback function to run when the event is triggered. The events available are listed on the [official documentation](https://g2.antv.vision/en/docs/api/general/event). 

If the callback function is `NULL` (default) then one that sets a shiny input is generated. The shiny input it generates is the id of the plot followed by the name of the event (where `:` is replaced with `_`). For instance, a point click event (`point:click`) for the plot with an id of `plotty` will be available at the following input: `input$plotty_point_click`.

```r
library(g2r)
library(shiny)

ui <- fluidPage(
  g2Output("g2plot"),
  p("Point clicked:"),
  verbatimTextOutput("clicked")
)

server <- function(input, output){

  output$g2plot <- renderG2({
    g2(cars, asp(dist, speed)) %>% 
      fig_point() %>% 
      fig_smooth() %>% 
      capture_event("element:click")
  })

  output$clicked <- renderPrint({
    print(input$g2plot_element_click)
  })

}

shinyApp(ui, server)
```

## JavaScript

Note that those events are always fired and can thus be used outside of Shiny: clicking a point on the chart below shows an alert.

```{r}
alert <- htmlwidgets::JS(
  "(ev) => {
    alert('You clicked a point with speed:' + ev.data.data.speed)
  }"
)

g2(cars, asp(speed, dist)) %>% 
  fig_point() %>% 
  capture_event("point:click", alert)
```
