---
title: "Tooltip"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tooltip}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(g2r)

motif_global(fontFamily = "Quicksand")
```

G2.js provides a custom tooltip but often times one might want to customise it.

## Default

```{r}
data(penguins, package = "palmerpenguins") 

g2(penguins, asp(bill_length_mm, bill_depth_mm, color = species)) %>% 
  fig_point(asp(shape = "circle")) %>% 
  gauge_color(c("#0C59FE", "#FEC700", "#FC0F00"))
```

## Global

The global tooltip can be customised with the `tooltip` function. This means applying changes to all tooltips, of all figures.

```{r}
penguins %>% 
  g2(asp(bill_length_mm, bill_depth_mm, color = species)) %>% 
  fig_point(asp(shape = "circle")) %>% 
  gauge_color(c("#0C59FE", "#FEC700", "#FC0F00")) %>% 
  tooltip(title = "Penguins!")
```

This can be used to remove the marker that shows on-hover.

```{r}
df <- data.frame(x = letters, y = runif(26))

g2(df, asp(x, y)) %>% 
  fig_interval() %>% 
  tooltip(showMarkers = FALSE)
```

## Aspects

One somewhat confusing thing perhaps is that the `tooltip` aspect can be used multiple times: G2.js allows using multiple columns from the dataset in the tooltip, including columns that are not used elsewhere.

```{r}
g2(penguins, asp(bill_length_mm, bill_depth_mm, color = species)) %>% 
  fig_point(
    asp(
      shape = "circle", 
      tooltip = island,
      tooltip = bill_length_mm,
      tooltip = bill_depth_mm
    )
  ) %>% 
  gauge_color(c("#0C59FE", "#FEC700", "#FC0F00"))
```

## Template & Gauge

The `tooltip` aspect can be combined with a template and a gauge. The template should be passed to the `itemTpl` argument of the `tooltip` function. The DOM classes can be found [here](https://g2.antv.vision/en/docs/api/general/tooltip); the HTML template must be passed as a string.

There are also two convenience function to create such templates: `tpl`, and `tpl_item`.

```{r}
template <- tpl(
  tpl_item(
    island,
    bill_depth_mm
  )
)

cb <- htmlwidgets::JS(
  "(island, bill_depth_mm) => {
    return {
      island: island,
      bill_depth_mm: bill_depth_mm
    };
  }"
)

penguins %>% 
  g2(asp(bill_length_mm, bill_depth_mm, color = species), elementId = "x") %>% 
  fig_point(
    asp(
      shape = "circle",
      tooltip = island,
      tooltip = bill_depth_mm
    )
  ) %>% 
  gauge_color(c("#0C59FE", "#FEC700", "#FC0F00")) %>% 
  gauge_tooltip(cb) %>% 
  tooltip(itemTpl = template)
```
